---
title: "Publications"
format:
    html:
        page-layout: full
---

```{css, echo=FALSE}
.vert-align {
    margin: auto;
}

.embed-video {
    text-align: center;
}
```

```{r setup, include=FALSE}
#| echo: false
#| warning: false
#| message: false
knitr::opts_chunk$set(echo = FALSE)
source("load_data.R")
library(tools)
library(DT)
```

This page shows all the publications produced as part of these consortia. The list is searchable, and you can click the icon on any row to be taken to the journal webpage for the full paper.

```{r list-publications}
#| results: 'asis'
#| echo: false

svg_string <- '<svg xmlns="http://www.w3.org/2000/svg" width="16" height="16" fill="currentColor" class="bi bi-link" viewBox="0 0 16 16">
  <path d="M6.354 5.5H4a3 3 0 0 0 0 6h3a3 3 0 0 0 2.83-4H9c-.086 0-.17.01-.25.031A2 2 0 0 1 7 10.5H4a2 2 0 1 1 0-4h1.535c.218-.376.495-.714.82-1z"/>
  <path d="M9 5.5a3 3 0 0 0-2.83 4h1.098A2 2 0 0 1 9 6.5h3a2 2 0 1 1 0 4h-1.535a4.02 4.02 0 0 1-.82 1H12a3 3 0 1 0 0-6H9z"/>
</svg>'

publications_table <- lapply(publication_list, function(pub) {
    data.frame(
        
        Date = pub$date,
        Link = glue::glue("<a href={pub$link}>{svg_string}</a>"),
        Citation = markdown::mark_html(
            text = pub$citation, 
            template = FALSE
        ) |>
            stringr::str_replace('(\r\n|\n).*', '') |>
            stringr::str_replace_all('<p>|</p>', '')
    )
}) |> bind_rows()

DT::datatable(
    publications_table, 
    rownames = FALSE, 
    escape = FALSE,
    colnames = c("Date", "Link", "Citation"),
    options = list(
        columnDefs = list(
            list(width = '100px', targets = 0),
            list(className = "dt-center", targets = c(0,1)),
            list(className = "vert-align", targets = 2)
        )
    )
)
```

## Video and Media

#### Press conference - Final Report to National Cabinet - Monday, 8 November 2021

::: {.embed-video}

<iframe width="560" height="315" src="https://www.youtube.com/embed/A93yEgz4Dc0" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

:::

#### Press conference - Monday, 20 September 2021

::: {.embed-video}

<iframe width="560" height="315" src="https://www.youtube.com/embed/w8hiINbSXa0" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

:::

#### Press conference - Doherty Institute Modelling Report for National Cabinet - Tuesday, 3 August 2021

::: {.embed-video}

<iframe width="560" height="315" src="https://www.youtube.com/embed/ubD9BZQKaWw" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture; web-share" allowfullscreen></iframe>

:::

#### Podcast - Doherty Institute Modelling

::: {.embed-video}

<iframe allow="autoplay" frameborder="0" height="190" scrolling="no" src="https://webplayer.whooshkaa.com/episode/888100?theme=light&amp;enable-volume=true&amp;iframe-height=190" width="100%" data-gtm-yt-inspected-31386276_19="true"></iframe>

:::

## Articles

* [Your unvaccinated friend is roughly 20 times more likely to give you COVID](https://theconversation.com/your-unvaccinated-friend-is-roughly-20-times-more-likely-to-give-you-covid-170448) - The Conversation